Bayesian MCMC diagnostics and summarisation using Tracer 1.6

### 2017-08-03 manuscript/tracer16.tex
smoother intro for demo reconstruction

>>>>

A key feature of Tracer lies in its ability to link together samples from quantitative random variable log files and tree log files.
This linkage is not available other popular post-processing MCMC software, such as coda \cite{citeref}, and enables users to approximate the posterior distribution of scientifically relevant quantities that are functions of both the tree and other quantitative measures.
Demographic reconstruction through time is a prime example.
